Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2010-10-26 paper/main.tex
More on face recognition...

Significant strides have been made in automatic face recognition by re-casting
it as a sparse representation problem.  This core of this algorithm consists of
stacking the test image into a vector $\y$, stacking the training images for
all of the users into the columns of a matrix $A$, and solving the following
minimization problem:
\begin{equation}
\min_{\x, \e} \| \x \|_1 + \|\e\|_1 \quad \subj \quad \y = A \x + \e.
\end{equation}
This optimization promotes a solution that is sparse both in $\x$ and $\e$. 
Sparsity in $\x$ arrises from the fact that only a subset of the training images (if any)
correspond to the user in the test image.  Sparsity in $\e$ arrises from the knowledge
that small occlusions in the test image will only corrupt a small subset of the pixels \cite{Wright2009-PAMI}.
The large coefficients in $\x$ will concentrate on the correct user, and can be used as the basis of a classifier.

@@

\section{Application to Face Recognition}
\begin{algorithm}[thb]
\caption{\bf (Deformable Sparse Recovery and Classification for
Face Recognition)} \label{alg:deformable-src}
\begin{algorithmic}[1]
\STATE {\bf Input:} Frontal training images $A_i \in \Re^{m\times n_i}, i=1,2,\ldots,K$ for $K$ subjects,  a test image
$\y\in\Re^m$ and a deformation group $T$. 
\STATE
{\bf for} each subject $i$, 
\STATE \hspace{3mm} $\tau^{(0)}
\leftarrow I$. 
\STATE \hspace{3mm} {\bf while} not converged $(j=1,2,\ldots)$ {\bf do} 
\STATE \hspace{6mm}
$\tilde \y(\tau) \leftarrow \frac{\y \circ \tau}{\|\y \circ
\tau\|_2}$; \;\;\; $J \leftarrow  \frac{\partial}{\partial
\tau} \tilde\y(\tau)  \bigr|_{\tau^{(j)}} $;
%\STATE \hspace{6mm} $(\hat \x, \hat \e, \Delta \tau) \leftarrow \left\{\begin{array}{l} \arg \min_{\x,\e,\Delta \tau} \| \e \|_1 \\  \subj \; \y + J \Delta \tau = A_k \x + \e \end{array}\right.$
\STATE \hspace{6mm} $ \Delta \tau =  \arg\min \; \| \e \|_1  \;
\subj \; \tilde \y + J \Delta \tau = A_i \x + \e.$ 
\STATE
\hspace{6mm} $\tau^{(j+1)} \leftarrow \tau^{(j)} + \Delta
\tau$; 
\STATE \hspace{3mm} {\bf end while} \STATE {\bf end} \STATE Keep
the top $S$ candidates $k_1, \ldots, k_S$ with the smallest
residuals $\|\e\|_1$. \STATE Compute an average transformation
$\bar{\tau}$ from $\tau_{k_1}, \tau_{k_2}, \ldots, \tau_{k_S}$.
\STATE Update $\y \leftarrow \y \circ \bar{\tau}$ and $\tau_i
\leftarrow \tau_i \cdot \bar{\tau}^{-1}$ for $i = k_1, \dots,
k_S$. \STATE Set $A \leftarrow \big[ A_{k_1} \circ
\tau_{k_1}^{-1} \mid A_{k_2} \circ \tau_{k_2}^{-1} \mid \dots
\mid A_{k_S} \circ \tau_{k_S}^{-1} \big]$. \STATE Solve the
$\ell^1$-minimization problem:
$$\hat{\x} = \arg \min_{\x, \e} \| \x \|_1 + \|\e\|_1 \;\; \subj \;\; \y = A \x + \e.$$
\STATE Compute residuals $r_i(\y) = \| {\y} - {A}_i \, \delta_i(\hat{\x}) \|_2$ for $i = k_1, \dots, k_S$.
\STATE {\bf Output:} $\mbox{identity}(\y) = \arg\min_i r_i(\y)$.
\end{algorithmic}
\end{algorithm}

>>>>

@@

\section{Application to Face Recognition}

Significant strides have been made in automatic face recognition by re-casting
it as a sparse representation problem.  This core of this algorithm consists of
Significant strides have been made in automatic face recognition by re-casting
it as a sparse representation problem.  This core of this algorithm consists of
stacking the test image into a vector $\y$, stacking the training images for
all of the users into the columns of a matrix $A$, and solving the following
minimization problem:
\begin{equation}
\min_{\x, \e} \| \x \|_1 + \|\e\|_1 \quad \subj \quad \y = A \x + \e.
\end{equation}
This optimization promotes a solution that is sparse both in $\x$ and $\e$. 
Sparsity in $\x$ arrises from the fact that only a subset of the training images (if any)
correspond to the user in the test image.  Sparsity in $\e$ arrises from the knowledge
that small occlusions in the test image will only corrupt a small subset of the pixels \cite{Wright2009-PAMI}.
The large coefficients in $\x$ will concentrate on the correct user, and can be used as the basis of a classifier.

For this idea to work, all of the images must be aligned. \cite{Wagner2009-CVPR}
For iterative alignment, we need to perform the following optimization problem:
\begin{equation}
\min_{\x, \e} \|\e\|_1 \quad \subj \quad \y = A \x + \e.
\end{equation}
stacking the test image into a vector $\y$, stacking the training images for
all of the users into the columns of a matrix $A$, and solving the following
minimization problem:
\begin{equation}
\min_{\x, \e} \| \x \|_1 + \|\e\|_1 \quad \subj \quad \y = A \x + \e.
\end{equation}
This optimization promotes a solution that is sparse both in $\x$ and $\e$. 
Sparsity in $\x$ arrises from the fact that only a subset of the training images (if any)
correspond to the user in the test image.  Sparsity in $\e$ arrises from the knowledge
that small occlusions in the test image will only corrupt a small subset of the pixels \cite{Wright2009-PAMI}.
The large coefficients in $\x$ will concentrate on the correct user, and can be used as the basis of a classifier.

\begin{algorithm}[thb]
\caption{\bf (Deformable Sparse Recovery and Classification for
Face Recognition)} \label{alg:deformable-src}
\begin{algorithmic}[1]
\STATE {\bf Input:} Frontal training images $A_i \in \Re^{m\times n_i}, i=1,2,\ldots,K$ for $K$ subjects,  a test image
$\y\in\Re^m$ and a deformation group $T$. 
\STATE
{\bf for} each subject $i$, 
\STATE \hspace{3mm} $\tau^{(0)}
\leftarrow I$. 
\STATE \hspace{3mm} {\bf while} not converged $(j=1,2,\ldots)$ {\bf do} 
\STATE \hspace{6mm}
$\tilde \y(\tau) \leftarrow \frac{\y \circ \tau}{\|\y \circ
\tau\|_2}$; \;\;\; $J \leftarrow  \frac{\partial}{\partial
\tau} \tilde\y(\tau)  \bigr|_{\tau^{(j)}} $;
%\STATE \hspace{6mm} $(\hat \x, \hat \e, \Delta \tau) \leftarrow \left\{\begin{array}{l} \arg \min_{\x,\e,\Delta \tau} \| \e \|_1 \\  \subj \; \y + J \Delta \tau = A_k \x + \e \end{array}\right.$
\STATE \hspace{6mm} $ \Delta \tau =  \arg\min \; \| \e \|_1  \;
\subj \; \tilde \y + J \Delta \tau = A_i \x + \e.$ 
\STATE
\hspace{6mm} $\tau^{(j+1)} \leftarrow \tau^{(j)} + \Delta
\tau$; 
\STATE \hspace{3mm} {\bf end while} \STATE {\bf end} \STATE Keep
the top $S$ candidates $k_1, \ldots, k_S$ with the smallest
residuals $\|\e\|_1$. \STATE Compute an average transformation
$\bar{\tau}$ from $\tau_{k_1}, \tau_{k_2}, \ldots, \tau_{k_S}$.
\STATE Update $\y \leftarrow \y \circ \bar{\tau}$ and $\tau_i
\leftarrow \tau_i \cdot \bar{\tau}^{-1}$ for $i = k_1, \dots,
k_S$. \STATE Set $A \leftarrow \big[ A_{k_1} \circ
\tau_{k_1}^{-1} \mid A_{k_2} \circ \tau_{k_2}^{-1} \mid \dots
\mid A_{k_S} \circ \tau_{k_S}^{-1} \big]$. \STATE Solve the
$\ell^1$-minimization problem:
$$\hat{\x} = \arg \min_{\x, \e} \| \x \|_1 + \|\e\|_1 \;\; \subj \;\; \y = A \x + \e.$$
\STATE Compute residuals $r_i(\y) = \| {\y} - {A}_i \, \delta_i(\hat{\x}) \|_2$ for $i = k_1, \dots, k_S$.
\STATE {\bf Output:} $\mbox{identity}(\y) = \arg\min_i r_i(\y)$.
\end{algorithmic}
\end{algorithm}
